Giant Low Surface Brightness Galaxies As Merger Remnants

### 2016-02-06 glsb.tex
update plot
huh
minor fiddles

%/astro/store/shared-scratch1/yoachim/Research/GLSB/THINGS/thingsplot.py
\begin{figure*}
\epsscale{.5}
\plotone{Plots/things.eps}
\epsscale{1}
\caption{ Comparison of the GLSB disks with other galaxy disks from the literature.  THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Galaz15}, Malin 2 and UGC 6614 from \citet{Pickering97}.  Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies, Malin~2, and UGC~6614 and the maximum radius with a stellar flux detection for Malin~1 XXX.  These are all maximum detection radii, and thus should be considered lower limits.  XXX--add in the stellar disks for Malin 2 and UGC 6614. \citet{Kasparova14} trace the light out to 60\arcsec on Malin~2, so 56 kpc\label{disk_comp}.  I trace UGC 6614 out to 65\arcsec, so 29 kpc.}
\end{figure*}

@@

%Some relevant papers for comparison:
%\citet{Weij09} use SAURON to get way out.  \citet{Proctor09} use Keck.  \citet{Murphy2011} use VP.
%$R_e = 7.3$\arcsec for UGC06614\\
%$R_e = 7.17$\arcsec for Malin2

>>>>

% /Users/yoachim/Research/GLSB/THINGS/thingsplot.py
\begin{figure*}
\epsscale{.5}
\plotone{Plots/things.eps}
\epsscale{1}
\caption{ Comparison of the GLSB disks with other galaxy disks from the literature.  THINGS data taken from \citet{DeBlok2008}, Malin 1 from \citet{Galaz15}, Malin 2 and UGC 6614 from \citet{Pickering97}, \citet{Kasparova14}, and this paper.  Here, $R_{max}$ is the maximum radius with an \HI\ detection for the THINGS galaxies.  For the gLSB galaxies, the solid points show the maximum \HI\ detection radius and stars show the maximum detected stellar light radius.  These are all maximum detection radii, and thus should be considered lower limits.   \label{disk_comp}}
\end{figure*}

@@

%$R_e = 7.3$\arcsec for UGC06614\\
%$R_e = 7.17$\arcsec for Malin2
